---
title: "AnnotationBustR Tutorial "
author: "Samuel R. Borstein"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# 1: Introduction

This is a tutorial for the use of the R package AnnotationBustR. AnnotationBustR reads in sequences from GenBank and allows you to quickly extract specific parts and write them to FASTA files by searching through the annotations in the features table. In this tutorial we will cover the basics of how to use AnnotationBustR to extract sequences as well as to  

# 2: Installation
##2.1: Installation from CRAN
In order to install the stable CRAN version of the AnnotationBustR package:
```
install.packages("AnnotationBustR")
```
##2.2: Installation from GitHub
While we recommend use of the stable CRAN version of this package, we rcommend using the package `devtools` to temporarily install the development version of the package from GitHub if for any reason you wish to use it :
```
#Install 'devtools' if you do not already have it installed:
install.packages("devtools")

#Load the 'devtools' package and temporarily install the development version of AnnotationBustR from GitHub:

```



## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
